Rates of true polar wander in convecting planets

### 2014-02-09 tpw_rate.tex
Start adding some tables

\begin{equation}
\begin{aligned}
 \rho \left[ \frac{D \bf v}{D t} + \frac{d \bf \Omega}{dt} \times {\bf r} +  2 {\bf \Omega} \times {\bf v} + {\bf \Omega \times \Omega \times r} \right] \\ = - \nabla P + \nabla \cdot \left( \eta \nabla_s {\bf v} \right) + \rho {\bf g}
\label{navier_stokes}
\end{aligned}
\end{equation}

@@

Dimensional analysis of this system (c.f. \cite{barenblatt1996scaling}) requires seven nondimensional numbers to characterize it.

>>>>

\begin{equation}
\begin{aligned}
 \rho_0 \left[ \frac{D \bf v}{D t} + \frac{d \bf \Omega}{dt} \times {\bf r} +  2 {\bf \Omega} \times {\bf v} + {\bf \Omega \times \Omega \times r} \right] \\ = - \nabla P + \nabla \cdot \left( \eta \nabla_s {\bf v} \right) + \rho {\bf g}
\label{navier_stokes}
\end{aligned}
\end{equation}

@@

Dimensional analysis of this system (c.f. \cite{barenblatt1996scaling}) requires six nondimensional numbers to characterize it.

\begin{table}
\caption{Parameters for rotating mantle convection}
\label{parameters}
\begin{tabular}{@{}lcc}
Symbol & Definition\\
\hline
$R_i$ & inner radius \\
$R_o$ & outer radius \\
$\Omega_0$ & reference rotation rate \\
$\eta$ & viscosity \\
$\kappa$ & thermal diffusivity \\
$\alpha$ & thermal expansivity \\
$g_0$ & reference gravity \\
$\rho_0$ & reference density \\
$\Delta T$ & temperature difference \\ 
\end{tabular}
\end{table}

\begin{table}
\caption{Nondimensional numbers with approximate Earthlike values}
\label{nondim}
\begin{tabular}{@{}lcccc}
Symbol &  Number & Definition & Approximate value \\
\hline
Ra & Rayleigh &  $\rho_0 g_0 \alpha \Delta T R_o^3/\eta \kappa$ & $10^7$\\
Pr & Prandtl & $\eta/\rho_0 \kappa$ & $10^{23}$ \\
Ek & Ekman & $\eta/\rho_0 \Omega_0 R_{o}^2$ & $10^8$ \\
Fr & Froude & $\Omega_0^2 R_o/g_0$ & $10^{-3}$ \\
$\Gamma$ & Density deficit & $\alpha \Delta T$ & $10^{-2}$ \\
A & Aspect ratio & $R_i/R_o$ & $0.55$ \\
\end{tabular}
\end{table}
